\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Dictionarry \href{https://github.com/Dictionarry-Hub}{\textcolor{black}{\faGithub}}}{React, Next.js, Python (Flask), Git, Docker, SQLite}
{Creator \& Lead Architect}{April 2023 - Present}
\resumeItemListStart
\resumeItem{Spearheaded Dictionarry, an \emph{open-source ecosystem} simplifying media automation for Radarr/Sonarr users via data-driven documentation, custom configurations, and integrated tooling.}
\vspace{3pt} % Add spacing after first item
\resumeItem{\textbf{Profilarr:} Architected and led development of Profilarr (\href{https://github.com/Dictionarry-Hub/profilarr}{\textcolor{black}{\faGithub}}), a \emph{full-stack} (React, Flask) configuration management tool (\emph{100,000+ Docker pulls}, \emph{800+} GitHub stars). Engineered its core \emph{git-based synchronization} and a novel \emph{compilation engine} to translate standardized configurations into application-specific syntaxes, enabling robust versioning and user customization.}
\vspace{3pt} % Add spacing after second item
\resumeItem{\textbf{Database:} Designed and implemented the Dictionarry Database (\href{https://github.com/Dictionarry-Hub/database}{\textcolor{black}{\faGithub}}) (\emph{20,000+} unique clones, \emph{60+} GitHub stars), establishing a \emph{"single definition" standard} for configurations. Developed data-driven systems like the \emph{Encode Efficiency Index (EEi)} with k-means clustering and the Golden Popcorn Performance Index (GPPi) to objectively rank media. Its design has inspired numerous forks (\emph{70+}) and fostered wider community sharing of novel configurations.}
\vspace{3pt} % Add spacing after third item
\resumeItem{\textbf{Web Platform:} Developed the Dictionarry web platform (\href{https://dictionarry.dev/}{dictionarry.dev}, \href{https://github.com/Dictionarry-Hub/website}{\textcolor{black}{\faGithub}}) (Next.js) as dynamic, self-updating documentation for the database, using \emph{Incremental Static Regeneration (ISR)}. Features an interactive Profile Builder to simplify user selection of complex configurations.}
\vspace{3pt} % Add spacing after fourth item
\resumeItem{\textbf{Community Management:} Cultivated and managed a vibrant Discord community of \emph{800+ members}. This involved coordinating moderators and contributors, handling pull requests, feature requests, and issues, providing technical support, and enhancing engagement with a custom \emph{Discord bot} interfacing with the Dictionarry ecosystem.}
\resumeItemListEnd
\resumeSubHeadingListEnd