% sections/projects.tex
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{OMesh (\href{https://github.com/santiagosayshey/OMesh}{GitHub})}{Python, Docker, WebSockets}
{Secure Messaging Platform}{}
\resumeItemListStart
\resumeItem{Built end-to-end encrypted messaging platform using low-level socket programming and custom protocol design.}
\vspace{2pt}
\resumeItem{Implemented RSA/AES-GCM cryptographic pipeline for secure key exchange and message encryption.}
\vspace{2pt}
\resumeItem{Deployed multi-server architecture with Docker Compose; real-time communication via WebSockets.}
\resumeItemListEnd
\resumeSubheading
{Synapsis (\href{https://github.com/SynapsisAI}{GitHub})}{React, Express, LLMs, FFmpeg}
{AI Research Paper Video Platform}{}
\resumeItemListStart
\resumeItem{Built full-stack platform using Grobid for paper parsing, LLMs for summarization/image generation, and FFmpeg for video synthesis.}
\vspace{2pt}
\resumeItem{Pitched at \textbf{Tech eChallenge} startup competition; ranked \textbf{Top 5} out of 50+ teams.}
\resumeItemListEnd
\resumeSubheading
{Rogue (\href{https://github.com/santiagosayshey/Rogue}{GitHub})}{C++, SFML}
{Procedural Roguelike Game}{}
\resumeItemListStart
\resumeItem{Built turn-based roguelike with procedural map generation and entity component system architecture.}
\vspace{2pt}
\resumeItem{Implemented design patterns (Factory, Observer, State) for extensible game object behavior.}
\resumeItemListEnd
\resumeSubheading
{Episode Splitter (\href{https://github.com/santiagosayshey/spongebob-split}{GitHub})}{Python, scipy, FFmpeg}
{Audio Cross-Correlation Tool}{}
\resumeItemListStart
\resumeItem{Built tool using audio cross-correlation to automatically detect episode boundaries in multi-episode files with millisecond precision—processing 146 episodes in 20 minutes vs weeks manually.}
\resumeItemListEnd
\resumeSubHeadingListEnd